Article Title

### 2019-08-30 Paper.tex
Set up proper citations
List of Authors (preliminary)

\def\Authors{
  First Author\,\textsuperscript{1},
  Co-Author\,\textsuperscript{2},
  Co-Author\,\textsuperscript{1,3*}}

@@

  \textsuperscript{1} Department X, Institution X,  City X,  State XX,  Country X

  \textsuperscript{2} Department X, Institution X,  City X,  State XX,  Country X

  \textsuperscript{3} Department X, Institution X,  City X,  State XX,  Country X
  }

  \def\firstAuthorLast{LASTNAME {et~al.}}

  \def\corrAuthor{Co-Author}\def\corrAddress{Laboratory X, Institute X, Department X, Organization X\\Street X\\City X, State XX, Zip Code X Country X}\def\corrEmail{\href{mailto:email@uni.edu}{\nolinkurl{email@uni.edu}}}

@@

@@

@@

\caption{\label{tab:quality-table}Quality evaluation of the used GO annotation sets.}
\centering
\begin{tabular}{llr}
\toprule
Genome & Dataset & SimGIC2 score\\
\midrule
\rowcolor{gray!6}   & GOMAP & 0.248394\\

 & GoldStandard & 0.999974\\

\rowcolor{gray!6}   & Gramene61-IEA & 0.319345\\

\multirow{-4}{*}{\raggedright\arraybackslash \textit{Oryza sativa}} & Gramene61-all & 0.732175\\
\cmidrule{1-3}
\rowcolor{gray!6}   & GOMAP & 0.024565\\

 & GoldStandard & 0.996264\\

\rowcolor{gray!6}   & Gramene49 & 0.043521\\

\multirow{-4}{*}{\raggedright\arraybackslash \textit{Zea mays} B73.v3} & Phytozome & 0.021982\\
\bottomrule
\end{tabular}
\end{table}

>>>>

\def\Authors{
  Dennis Psaroudakis\,\textsuperscript{1},
  Ha Vu\,\textsuperscript{1},
  Colleen Yanarella\,\textsuperscript{1},
  Steven Cannon\,\textsuperscript{1},
  Darwin Campbell\,\textsuperscript{1},
  Parnal Joshi\,\textsuperscript{1},
  Iddo Friedberg\,\textsuperscript{1,4},
  Kokulapalan Wimalanathan\,\textsuperscript{1,2},
  Carolyn J. Lawrence-Dill\,\textsuperscript{1,2,3*}}

@@

  \textsuperscript{1} Bioinformatics and Computational Biology, Iowa State University,  Ames,  IA,  USA

  \textsuperscript{2} Department of Genetics, Development, and Cell Biology, Iowa State University,  Ames,  IA,  USA

  \textsuperscript{3} Department of Agronomy, Iowa State University,  Ames,  IA,  USA

  \textsuperscript{4} Department of Veterinary Microbiology, Iowa State University,  Ames,  IA,  USA
  }

  \def\firstAuthorLast{Psaroudakis {et~al.}}

  \def\corrAuthor{Carolyn J. Lawrence-Dill}\def\corrAddress{Roy J. Carver Co-Lab, Iowa State University\\1111 WOI Rd\\Ames, State IA, 50011 USA}\def\corrEmail{\href{mailto:triffid@iastate.edu}{\nolinkurl{triffid@iastate.edu}}}

@@

\hypertarget{choosing-the-right-evaluation-metric}{%
\subsection{Choosing the right evaluation metric}\label{choosing-the-right-evaluation-metric}}

A plethora of different metric to evaluate the quality of functional annotation predictions is available using different approaches and there seems to be no clear standard yet. \texttt{TODO:\ THIS\ IS\ WEAK}
Additionally, each of the metrics has a different focus and lalala so choosing a metric for quality evaluation is not trivial.
When we first published GOMAP \citep{Wimalanathan2018}, we used a modified version of the hierarchical evaluation metrics originally introduced in \citep{Verspoor2006} because they were simple, clear, and part of an earlier attempt at unifying and standardizing GO annotation comparisons \citep{Defoin-Platel2011}.
In the meantime, \citet{Plyusnin2018} have published an approach for evaluating different metrics showing substantial differences within the robustness of different approaches.
\texttt{TODO\ DESCRIBE\ THEIR\ APPROACH}
We have applied their method on the Gold Standards available to us to determine which evaluation metric is the most appropriate in our case.
The results of this analysis can be seen in \texttt{TODO}.

We then evaluated our predictions and the other annotation sets using the best performing metrics as well as the one we previously used.
\texttt{TODO}

@@

\hypertarget{quality-evaluation}{%
\subsection{Quality Evaluation}\label{quality-evaluation}}

\texttt{TODO} If it turns out that our predictions are good with hF but bad with more approriate metrics, explanation would be that score thresholds for the prediction tools used in the GOMAP pipeline have been chosen to maximize this hF value. It now seems reasonable to re-adjust these thresholds to maximize a different metric which will likely result in a drop in hF score but increase in other metrics. Again emphasizes the importance of choosing the right evaluation metric.

@@

\caption{\label{tab:quality-table}Quality evaluation of the used GO annotation sets.}
\centering
\begin{tabular}{llr}
\toprule
Genome & Dataset & SimGIC2 score\\
\midrule
\rowcolor{gray!6}   & GOMAP & 0.241470\\

 & GoldStandard & 0.999971\\

\rowcolor{gray!6}   & Gramene61-IEA & 0.324831\\

\multirow{-4}{*}{\raggedright\arraybackslash \textit{Oryza sativa}} & Gramene61-all & 0.732289\\
\cmidrule{1-3}
\rowcolor{gray!6}   & GOMAP & 0.072971\\

 & GoldStandard & 0.998562\\

\rowcolor{gray!6}   & Gramene49 & 0.126450\\

\multirow{-4}{*}{\raggedright\arraybackslash \textit{Zea mays} B73.v3} & Phytozome & 0.032693\\
\bottomrule
\end{tabular}
\end{table}

\bibliography{GOMAP-Paper-Used}

### 2019-08-30 text/03-results.Rmd
Set up proper citations
List of Authors (preliminary)

>>>>

## Quality Evaluation

`TODO` If it turns out that our predictions are good with hF but bad with more approriate metrics, explanation would be that score thresholds for the prediction tools used in the GOMAP pipeline have been chosen to maximize this hF value. It now seems reasonable to re-adjust these thresholds to maximize a different metric which will likely result in a drop in hF score but increase in other metrics. Again emphasizes the importance of choosing the right evaluation metric.

### 2019-08-30 text/index.Rmd
List of Authors (preliminary)

---
title: "Article Title"
runtitle: "Short Title"
documentclass: frontiersSCNS  # or frontiersHLTH, or frontiersFPHY
author:
  - name: First Author
    affiliation: '1'
    etal: LASTNAME # First author's last name. 
  - name: Co-Author
    affiliation: '2'
  - name: Co-Author
    affiliation: '1,3'
    email: email@uni.edu # Indicates corresponding Author
    institution: Laboratory X, Institute X, Department X, Organization X
    street: Street X
    city: City X
    state: State XX # only USA, Australia, Canada
    zip: Zip Code X
    country: Country X
affiliation:
  - id: '1'
    department: Department X
    institution: Institution X
    city: City X
    state: State XX # only USA, Australia, Canada
    country: Country X
  - id: '2' 
    department: Department X
    institution: Institution X
    city: City X
    state: State XX # only USA, Australia, Canada
    country: Country X
  - id: '3' 
    department: Department X
    institution: Institution X
    city: City X
    state: State XX # only USA, Australia, Canada
    country: Country X
date: "Febcember 32nd 3023"
language: en-US
site: "bookdown::bookdown_site"
csl: frontiers.csl
link-citations: true
output:
  bookdown::pdf_book:
    keep_tex: true
    keep_md: true
    base_format: rticles::frontiers_article
    citation_package: natbib
    includes:
      in_header:
        preamble.tex
---

>>>>

---
title: "Article Title"
runtitle: "Short Title"
documentclass: frontiersSCNS  # or frontiersHLTH, or frontiersFPHY
author:
  - name: Dennis Psaroudakis
    affiliation: '1'
    etal: Psaroudakis # First author's last name. 
  - name: Ha Vu
    affiliation: '1'
  - name: Colleen Yanarella
    affiliation: '1'
  - name: Steven Cannon
    affiliation: '1'
  - name: Darwin Campbell
    affiliation: '1'
  - name: Parnal Joshi
    affiliation: '1'
  - name: Iddo Friedberg
    affiliation: '1,4'
  - name: Kokulapalan Wimalanathan
    affiliation: '1,2'
  - name: Carolyn J. Lawrence-Dill
    affiliation: '1,2,3'
    email: triffid@iastate.edu
    institution: Roy J. Carver Co-Lab, Iowa State University
    street: 1111 WOI Rd
    city: Ames
    state: State IA # only USA, Australia, Canada
    zip: 50011
    country: USA
affiliation:
  - id: '1'
    department: Bioinformatics and Computational Biology
    institution: Iowa State University
    city: Ames
    state: IA # only USA, Australia, Canada
    country: USA
  - id: '2'
    department: Department of Genetics, Development, and Cell Biology
    institution: Iowa State University
    city: Ames
    state: IA # only USA, Australia, Canada
    country: USA
  - id: '3'
    department: Department of Agronomy
    institution: Iowa State University
    city: Ames
    state: IA # only USA, Australia, Canada
    country: USA
  - id: '4'
    department: Department of Veterinary Microbiology
    institution: Iowa State University
    city: Ames
    state: IA # only USA, Australia, Canada
    country: USA
date: "Febcember 32nd 3023"
language: en-US
site: "bookdown::bookdown_site"
csl: frontiers.csl
link-citations: true
output:
  bookdown::pdf_book:
    keep_tex: true
    keep_md: true
    base_format: rticles::frontiers_article
    citation_package: natbib
    includes:
      in_header:
        preamble.tex
---
